---
title: "Recruitment"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r,results='hide', message=FALSE}
rm(list=ls())
library(readxl)
library(tibble)
master_code_list <- read_excel("/home/cranilab/Documents/CRANI/Master_code_lists/master_code_list.xlsx")

smart_HC <- 50
smart_SZ <- 30
smart_MDD <- 20

cogrehab_HC <- 30
cogrehab_SZ <- 48
cogrehab_MDD <- 48

vr_SZ <- 40
```

***
<center><font size="4"> **OVERALL** </font> </center>
####*<span style="color:red">HC</span>*
#####*<span style="color:blue">total number of healthy controls that have been screened</span>*
```{r}
HC <- subset(master_code_list, Diagnosis == "N/A")
nrow(HC)
```
<br>

####*<span style="color:red">SZ</span>*
#####*<span style="color:blue">total number of schizophrenia/schizoaffective patients that have been screened</span>*
```{r}
SZ <- subset(master_code_list, substr(master_code_list$Diagnosis, 1, 2) == "Sc")
nrow(SZ) 
```
<br>

####*<span style="color:red">MDD</span>*
#####*<span style="color:blue">total number of depression patients that have been screened</span>*
```{r}
MDD <- subset(master_code_list, substr(master_code_list$Diagnosis, 1, 2) == "De")
nrow(MDD) 
```
<br>

####*<span style="color:red">OTHER</span>*
#####*<span style="color:blue">total number of people with other diagnoses</span>*
```{r}
Other <- subset(master_code_list, Diagnosis !="N/A" & substr(master_code_list$Diagnosis, 1, 2) != "Sc" & substr(master_code_list$Diagnosis, 1, 2) != "De")
nrow(Other)
```
<br>

#####*<span style="color:blue">list the diagnoses</span>*
```{r}
print(data.frame(Other$Screening_ID, Other$Diagnosis))
```
***
<center><font size="4"> **SMARTPHONE** </font> </center>
####*<span style="color:red">HC</span>*
#####*<span style="color:blue">number of healthy controls eligible to participate in smartphone study</span>*
```{r}
nrow(subset(HC, Smart_Inclusion == "Yes")) 
```
<br>

#####*<span style="color:blue">number of healthy controls NOT eligible to particiapte in smartphone study</span>*
```{r}
nrow(HC)-nrow(subset(HC, Smart_Inclusion == "Yes")) 
```
<br>

#####*<span style="color:blue">number of healthy controls particiapted in smartphone study</span>*
```{r}
nrow(subset(HC, Smart_ID != "NA")) 
```

<br>

#####*<span style="color:blue">number of additional healthy controls needed in smartphone study</span>*
```{r}
smart_HC-nrow(subset(HC, Smart_ID != "NA")) 
```


<br>

####*<span style="color:red">SZ</span>*
#####*<span style="color:blue">number of schizophrenia/schizoaffective patients eligible to participate in smartphone study</span>*
```{r}
nrow(subset(SZ, Smart_Inclusion == "Yes")) 
```
<br>

#####*<span style="color:blue">number of schizophrenia/schizoaffective patients NOT eligible to particiapte in smartphone study</span>*
```{r}
nrow(SZ)-nrow(subset(SZ, Smart_Inclusion == "Yes")) 
```
<br>

#####*<span style="color:blue">number of schizophrenia/schizoaffective patients particiapted in smartphone study</span>*
```{r}
nrow(subset(SZ, Smart_ID != "NA")) 
```
<br>

#####*<span style="color:blue">number of additional schizophrenia/schizoaffective patients needed in smartphone study</span>*
```{r}
smart_SZ-nrow(subset(SZ, Smart_ID != "NA")) 
```


<br>

####*<span style="color:red">MDD</span>*
#####*<span style="color:blue">number of depression patients eligible to participate in smartphone study</span>*
```{r}
nrow(subset(MDD, Smart_Inclusion == "Yes"))
```
<br>

#####*<span style="color:blue">number of depression patients NOT eligible to particiapte in smartphone study</span>*
```{r}
nrow(MDD)-nrow(subset(MDD, Smart_Inclusion == "Yes")) 
```
<br>

#####*<span style="color:blue">number of depression patients particiapted in smartphone study</span>*
```{r}
nrow(subset(MDD, Smart_ID != "NA")) 
```

<br>

#####*<span style="color:blue">number of additional depression patients needed in smartphone study</span>*
```{r}
smart_MDD-nrow(subset(MDD, Smart_ID != "NA")) 
```

***
<center><font size="4"> **VR PILOT** </font> </center>
####*<span style="color:red">SZ</span>*
#####*<span style="color:blue">number of schizophrenia/schizoaffective patients eligible to participate in VR pilot study</span>*
```{r}
nrow(subset(SZ, VR_Inclusion == "Yes"))
```
<br>

#####*<span style="color:blue">number of chizophrenia/schizoaffective patients NOT eligible to particiapte in VR pilot study</span>*
```{r}
nrow(SZ)-nrow(subset(SZ, VR_Inclusion == "Yes")) 
```
<br>

#####*<span style="color:blue">number of schizophrenia/schizoaffective patients particiapted in VR pilot study</span>*
```{r}
nrow(subset(SZ, VR_ID != "NA")) 
```

<br>

#####*<span style="color:blue">number of additional schizophrenia/schizoaffective patients needed in VR pilot study</span>*
```{r}
vr_SZ-nrow(subset(SZ, VR_ID != "NA")) 
```

***
<center><font size="4"> **COGREHAB** </font> </center>
####*<span style="color:red">HC</span>*
#####*<span style="color:blue">number of healthy controls eligible to participate in CogRehab</span>*
```{r}
nrow(subset(HC, CogRehab_Inclusion == "Yes")) 
```
<br>

#####*<span style="color:blue">number of healthy controls NOT eligible to particiapte in CogRehab</span>*
```{r}
nrow(HC)-nrow(subset(HC, CogRehab_Inclusion == "Yes")) 
```
<br>

#####*<span style="color:blue">number of healthy controls particiapted in CogRehab</span>*
```{r}
nrow(subset(HC, CogRehab_ID != "NA")) 
```
<br>

#####*<span style="color:blue">number of additional healthy controls needed in CogRehab</span>*
```{r}
cogrehab_HC-nrow(subset(HC, CogRehab_ID != "NA")) 
```


<br>

####*<span style="color:red">SZ</span>*
#####*<span style="color:blue">number of schizophrenia/schizoaffective patients eligible to participate in CogRehab</span>*
```{r}
nrow(subset(SZ, CogRehab_Inclusion == "Yes")) 
```
<br>

#####*<span style="color:blue">number of schizophrenia/schizoaffective patients NOT eligible to particiapte in CogRehab</span>*
```{r}
nrow(SZ)-nrow(subset(SZ, CogRehab_Inclusion == "Yes")) 
```
<br>

#####*<span style="color:blue">number of schizophrenia/schizoaffective patients particiapted in CogRehab</span>*
```{r}
nrow(subset(SZ, CogRehab_ID != "NA")) 
```

<br>

#####*<span style="color:blue">number of additional schizophrenia/schizoaffective patients needed in CogRehab</span>*
```{r}
cogrehab_SZ-nrow(subset(SZ, CogRehab_ID != "NA")) 
```


<br>

####*<span style="color:red">MDD</span>*
#####*<span style="color:blue">number of depression patients eligible to participate in CogRehab</span>*
```{r}
nrow(subset(MDD, CogRehab_Inclusion == "Yes"))
```
<br>

#####*<span style="color:blue">number of depression patients NOT eligible to particiapte in CogRehab</span>*
```{r}
nrow(MDD)-nrow(subset(MDD, CogRehab_Inclusion == "Yes")) 
```
<br>

#####*<span style="color:blue">number of depression patients particiapted in CogRehab</span>*
```{r}
nrow(subset(MDD, CogRehab_ID != "NA")) 
```
<br>

#####*<span style="color:blue">number of additional depression patients needed in CogRehab</span>*
```{r}
cogrehab_MDD-nrow(subset(MDD, CogRehab_ID != "NA")) 
```


***
<center><font size="4"> **REASONS FOR EXCLUSION** </font> </center>
####*<span style="color:red">HC</span>*
```{r}
HC_EX <- subset(HC, CogRehab_Inclusion != "Yes" | Smart_Inclusion != "Yes")
print(tibble(HC_EX$Screening_ID, HC_EX$CogRehab_Inclusion, HC_EX$Smart_Inclusion))
```
<br>

####*<span style="color:red">SZ</span>*
```{r}
SZ_EX <- subset(SZ, CogRehab_Inclusion != "Yes" | Smart_Inclusion != "Yes" | VR_Inclusion != "Yes")
print(tibble(SZ_EX$Screening_ID, SZ_EX$CogRehab_Inclusion, SZ_EX$Smart_Inclusion, SZ_EX$VR_Inclusion))
```
<br>

####*<span style="color:red">MDD</span>*
```{r}
MDD_EX <- subset(MDD, CogRehab_Inclusion != "Yes" | Smart_Inclusion != "Yes")
print(tibble(MDD_EX$Screening_ID, MDD_EX$CogRehab_Inclusion, MDD_EX$Smart_Inclusion))
```